Results

### 2025-06-09 notebooks/00_index.qmd
update

```{julia}
using Dates
using DrWatson
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using Discontinuity
```

@@

```{julia}
using Speasy
using SPEDAS: ulabel, smooth, tnorm_combine, tplot
using DimensionalData
# using CairoMakie
using GLMakie
using Statistics
using PartialFunctions
using Unitful
using Beforerr: _theme_legend, easy_save
using SPEDAS.SpaceDataModel: set, extend, @set
include("../src/psp_temp.jl")
include("../src/calc.jl")
include("../src/meta.jl")

@@

```{julia}
tvars_psp = [
    set(tnorm_combine ∘ PSP.B_1MIN; ylabel=B_ylabel, labels=B_RTN_labels),
    set(PSP.n; ylabel=n_ylabel),
    set(tnorm_combine ∘ PSP.V; ylabel=V_ylabel, labels=V_RTN_labels),
    set(PSP.T; ylabel=T_ylabel)
]
```

```{julia}
tvars_wind = [
    set(tnorm_combine ∘ Wind.B_RTN_1MIN; ylabel=B_ylabel, labels=B_RTN_labels),
    set(Wind.n; ylabel=n_ylabel),
    set(Wind.V_RTN; ylabel=V_ylabel, labels=V_RTN_labels),
    set(Wind.T; ylabel=T_ylabel)
]
```

```{julia}
using Intervals: Interval
data = THEMIS.V_GSE(tmin_wind, tmax_wind)
_times = @views SPEDAS.times(data)[(data[:, 1].>-200u"km/s").|(data[:, 2].<-50u"km/s")]
dt = Minute(10)
its = union([Interval(t - dt, t + dt) for t in _times])
_tmask! = tmask!(its)
```

```{julia}
tvars_themis = [
    set(_tmask! ∘ tnorm_combine ∘ THEMIS.B_GSE; ylabel=B_ylabel, labels=B_XYZ_labels),
    THEMIS.n,
    _tmask! ∘ THEMIS.V_GSE,
    set(THEMIS.T; ylabel=T_ylabel)
]

@@

tplot(f[1, 1], tvars_themis, tmin_wind, tmax_wind; legend)
add_labels!(f[1, 1]; labels, open="(c.")
f
# easy_save("overview")
```

>>>>

```{julia}
using Dates
using DrWatson
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using Discontinuity
using SPEDAS
```

@@

```{julia}
using Speasy
using SPEDAS: ulabel, smooth, tnorm_combine, tplot
using DimensionalData
using CairoMakie
# using GLMakie
using Statistics
using PartialFunctions
using Unitful
using Beforerr: _theme_legend, easy_save
using SPEDAS.SpaceDataModel: set, extend, @set
include("../src/psp_temp.jl")
include("../src/calc.jl")
include("../src/meta.jl")

@@

```{julia}
tvars_psp = [
    set(tnorm_combine ∘ PSP.B_1MIN; ylabel=B_ylabel, labels=B_RTN_labels),
    set(PSP.n; ylabel=n_ylabel),
    set(PSP.V; ylabel=V_ylabel, labels=V_RTN_labels),
    set(PSP.T; ylabel=T_ylabel)
]
```

```{julia}
tvars_wind = [
    set(tnorm_combine ∘ Wind.B_GSE; ylabel=B_ylabel),
    set(Wind.n; ylabel=n_ylabel),
    # set(Wind.V_GSE_p; ylabel=V_ylabel),
    replace_outliers! ∘ set(Wind.V_GSE_K0; ylabel=V_ylabel),
    set(Wind.T; ylabel=T_ylabel)
]
```

```{julia}
using GLMakie
```

```{julia}
using Intervals: Interval
thx_v_gse = THEMIS.V_GSE(tmin_wind, tmax_wind)
_times = @views SPEDAS.times(thx_v_gse)[(thx_v_gse[:, 1].>-200u"km/s").|(thx_v_gse[:, 2].<-50u"km/s")]
dt = Minute(10)
its = union([Interval(t - dt, t + dt) for t in _times])
_tmask! = tmask!(its)
```

```{julia}
tvars_themis = [
    set(_tmask! ∘ tnorm_combine ∘ THEMIS.B_GSE; ylabel=B_ylabel, labels=B_XYZ_labels),
    THEMIS.n,
    _tmask! ∘ THEMIS.V_GSE,
    set(_tmask! ∘ THEMIS.eTemp; ylabel=T_ylabel)
]

@@

tplot(f[1, 3], tvars_themis, tmin_wind, tmax_wind; legend)
add_labels!(f[1, 3]; labels, open="(c.")
f
# easy_save("overview")
```
